Measurement and Probability in Fuzzy Quantum Theories

### 2016-11-26 proposal/prop.tex
42

This is the most developed part of our current investigation and is
more detailed.

Just as it is the case for Buffon's needles, estimating quantum
probabilities (e.g., in the case of a Stern-Gerlach experiment) with
increasing accuracy requires increasingly large resources.  Therefore,
given some finite resources, it is only possible to estimate the
quantum probabilities within an interval of confidence. It is
therefore natural to introduce the notion of an ``interval-valued
quantum probability measure'' that combines the definitions of
conventional quantum probability measures with classical
interval-probabilities.

@@

It is easy to establish that quantum interval-valued probability
measures generalize conventional quantum probability measures. In
particular, any quantum probability measure can be recast as an
interval-valued measure using the three intervals $\left[0,0\right]$,
$\left[1,1\right]$ and \emph{$\left[0,1\right]$}, where
$\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called
\unknown~because it provides no information as follows. Given a
probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
define a quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where
$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{if }x=1\textrm{ ;}\\
\imposs & \textrm{if }x=0\textrm{ ;}\\
\unknown & \textrm{otherwise.}
\end{cases}
\]

The interesting question is the converse one corresponding to
Gleason's theorem. Given an interval-valued probability measure, i.e.,
given observations done with finite resources, do these observations
uniquely determine a quantum state? Our initial investigations
indicate that the answer is \emph{no}.

@@

>>>>

This is the most developed part of our current investigation and is
presented in great detail. As argued in the previous sections, given
fixed finite resources, it is only possible to estimate the quantum
probabilities within an interval of confidence. It is therefore
natural to propose the notion of an ``interval-valued quantum
probability measure'' that combines the definitions of conventional
quantum probability measures with classical interval-probabilities.

@@

\noindent It is easy to establish that quantum interval-valued
probability measures generalize conventional quantum probability
measures. In particular, any quantum probability measure can be recast
as an interval-valued measure using the three intervals
$\left[0,0\right]$, $\left[1,1\right]$ and \emph{$\left[0,1\right]$},
where $\left[0,0\right]$ and $\left[1,1\right]$ are called \imposs~and
\necess~as before, and \emph{$\left[0,1\right]$} is called
\unknown~because it provides no information. Given a quantum
probability measure~$\mu:\events\rightarrow\left[0,1\right]$, we
define a quantum interval-valued probability
measure~$\bar{\mu}:\events\rightarrow\mathscr{I}$ by
$\bar{\mu}(P)=\iota\left(\mu(P)\right)$, where
$\iota:\left[0,1\right]\rightarrow\mathscr{I}$ is defined by
\[
\iota(x)=\begin{cases}
\necess & \textrm{if }x=1\textrm{ ;}\\
\imposs & \textrm{if }x=0\textrm{ ;}\\
\unknown & \textrm{otherwise.}
\end{cases}
\]
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question. Formally,
we can ask: what can we deduce about the state of a quantum system
given an interval-valued quantum probability measure, i.e., given
observations done with finite resources. In the case the intervals are
infinitely precise the question reduces to Gleason's theorem which
states that the state of the quantum system is uniquely determined by
the probability measure. But surely the less resources are availble,
the less precise the intervals, and the less we expect to know about
the state of the system. To formally state and answer this question we
begin with defining the \emph{core} and \emph{convexity} of a
probability measure as follows.

@@

core: easy

convex: if certain intervals exist then combinations of these
intervals must also exist so that we can add probabilities etc. in the
classical case ... theorem but in the quantum case we found a counterexample

It is common to consider convex interval-valued probability measures.
For example, a special case of convex interval-valued probability
measures consists the Dempster-Shafer belief function as the left-end
and the Dempster-Shafer plausibility as the
right-end~\cite{Dempster1967,Shafer1976,GilboaSchmeidler1994,Goodman1997,Marinacci1999,Teran2014}.
Dempster-Shafer functions, also called \emph{completely} or
\emph{totally monotone}, play an important role in the theory of
non-additive belief.  Furthermore, convex interval-valued probability
measures have a good property that they can always be associated with
real-valued probability measures.

\begin{thm}[Shapley~\cite{Shapley1971}]\label{thm:Shapley}
Every convex interval-valued probability measure has a nonempty core.\qed\end{thm}
